### 2013-01-08 edupar-13/landslide.tex
Explain 'race condition' terminology

In general, with false-negative bug detection, the kernel might execute a buggy behaviour yet Landslide would miss it. However (except in the case of heuristic infinite loop detection), when Landslide does identify a bug, the student can be sure that a race exists.

>>>>

Note that our use of the term ``race condition'' refers to concurrency errors in general, a category that includes data races, atomicity violations, and nondeterministic deadlocks.
In contrast with analyses that directly detect data races~\cite{tsan}, Landslide does not identify bugs merely upon suspicious memory accesses, but rather detects failure conditions that can arise from many different types of errors.
In general, with false-negative bug detection, the kernel might execute a buggy behaviour yet Landslide would miss it. However (except in the case of heuristic infinite loop detection), when Landslide does identify a bug, the student can be sure that a race exists.
